\chapter{Conclusion and Future Work}
    \label{chap:conclusion}

    \section{Future Work}
    \label{sec:conclusion_future_work}
        In this section, the future work that could be done for this project will be outlined.  
    
        Application improvements could include adding Siri integration so that users can ask Siri to add an item to the application.  Support for widgets (which was introduced in iOS14) could also be added so items could be added to the application without needing to open it.  Apple Watch support could also be added so that the users' mobile device does not need to be in use at all in order to view, add and complete items.  In terms of existing features, the 'friends' view could be improved by adding messaging support and adding the recent activity feature that initially was planned in the requirements and design.
    
        The application could also be replicated as an Android application to support more mobile devices to increase universal support.
    
    \section{Conclusion}
    \label{sec:conclusion_conclusion}
        This project's objective was to create a productivity and time management application that would help users manage their tasks throughout their day, week and month, and encourage them to be more productive and deliberate with their time.  The application that has been produced meets these requirements; users can add items that can be set as habits, tasks, events, reminders or all of the above.  They have suggested tasks based on their day's schedule.  Users can view items in their native iOS calendar and use the application to set a focus timer.  Finally, users can connect with others and use other people's progress as motivation to complete their tasks.  The application is also entirely available for free and will remain free, and has much potential for more productivity features to be added over time, outlined in Section~\ref{sec:conclusion_future_work}.